Slitasje og kjørespor

### 2023-01-23 DRAFT_slitasjeOgKjørespor.Rmd
bug: Rearrange code blocks

```{r}
myBB <- st_bbox(c(xmin=260520.12, xmax = 278587.56,
                ymin = 7032142.5, ymax = 7045245.27),
                crs = st_crs(HIA))
```

```{r}
HIA <- sf::st_crop(HIA, myBB)
```

<!-- ERROR  marine areas still here -->
```{r}
tm_shape(HIA)+
  tm_polygons(col = "infrastructureIndex",
    title="Infrastructure index\n(modified 4-step scale)",
    palette = "viridis",
    style="cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")
```

@@

Let's calculate the areas of these polygons and compare the HIF in the
five regions. First we need to remove some marine areas.

```{r}
HIA_regions2 <- HIA_regions %>%
  st_intersection(outline)
```

```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
HIA_regions$area <- sf::st_area(HIA_regions)

temp <- as.data.frame(HIA_regions) %>%
  group_by(region, infrastructureIndex) %>%
  summarise(area = mean(area))

@@

>>>>

@@

```{r}
myBB <- st_bbox(c(xmin=260520.12, xmax = 278587.56,
                ymin = 7032142.5, ymax = 7045245.27),
                crs = st_crs(HIA_regions))
```

```{r}
HIA_trd <- sf::st_crop(HIA_regions, myBB)
```

```{r}
tm_shape(HIA_trd)+
  tm_polygons(col = "infrastructureIndex",
    title="Infrastructure index\n(modified 4-step scale)",
    palette = "viridis",
    style="cat")+
  tm_layout(legend.outside = T)+
  tm_shape(hw_utm)+
  tm_lines(col="blue")
```

Let's calculate the areas of these polygons and compare the HIF in the
five regions. 
```{r}
HIA_regions$area <- sf::st_area(HIA_regions)
```

```{r HIF-region, fig.cap="Stacked barplot showing the distribution of human impact factor across five regions in Norway."}
temp <- as.data.frame(HIA_regions) %>%
  group_by(region, infrastructureIndex) %>%
  summarise(area = mean(area))

@@

<!-- ERROR with summarise = T -->
```{r}
summary_temp <- ea_spread(indicator_data = slitasje_data,
                         indicator = i_2020,
                         regions = HIA_regions,
                         groups = region_HIF,
                         summarise = TRUE)
```
